% ============================================================
%  Stan (Aisling) Leiva-Davila — Pursuit AI Builder resume
%  PAPER SIZE: change ONE word on the next line.
%    letterpaper  -> US Letter (8.5 x 11)  [default for the website button]
%    legalpaper   -> US Legal  (8.5 x 14)
%  Margins below use \addtolength (relative), so both sizes work unchanged.
% ============================================================
\documentclass[letterpaper,10pt]{article}   % <-- swap letterpaper <-> legalpaper

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-.6in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.4in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingEd}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} &  \small #2\\
      \textit{\small#3} & \textit{\small #4}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small#3} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingShort}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
    \end{tabular*}\vspace{-5pt}
}

% Project subheading: name left, year right; description line; then github link right
\newcommand{\resumeProjectHeading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small #3} & \small \href{#4}{\faGithub} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
}

\usepackage{mathptmx}
\usepackage{setspace}
\usepackage{fontawesome}



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{center}{\textwidth}
  \textbf{{\Huge Stan (Aisling) Leiva-Davila}} \\ \medskip \smallskip
  {\large {ness.aisling@gmail.com} $|$ {aisling.ld@pursuit.org} $|$ 201-471-1178} \\ \smallskip
  {\large New York, NY $|$
  \faLinkedinSquare $ $ \href{https://www.linkedin.com/in/stan-leiva-davila/}{stan-leiva-davila} $|$
  \faGithub $ $ \href{https://github.com/nessaisling-lab}{nessaisling-lab}}
\end{center}

%-----------SUMMARY-----------------
\section{Professional Summary}
{\small Self-taught AI Builder and founder who ships production-grade systems solo and on small teams. Built a native-Rust financial-intelligence terminal (+37\% paper-trade ROI) and a privacy-first, on-device voice-to-text app — both cross-platform desktop products. Hardware-fluent (Aircraft A\&P coursework, CompTIA A+) with end-to-end ownership from systems and data pipelines through UI and go-to-market. Inaugural cohort of Pursuit's AI-Native Builder program.}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheadingEd
      {Nisaba Capital Charting $|$ Founder \& Builder}{Apr. 2026 -- Present}
      {Native-Rust financial-intelligence desktop terminal merging market data with a Hellenistic astrology engine.}{New York, NY}
      \resumeItemListStart
        \resumeItem{}
            {Built a $\sim$25k-line Rust application solo in 30 days — 12 data APIs, 10 native scrapers, 46 SQLx migrations, an axum REST sidecar, and a Swiss Ephemeris engine validated to sub-arcsecond precision; 132 tests, zero warnings, shipped a v12.2.0 Windows installer}
        \resumeItem{}
            {Reached +37.06\% verified paper-trade ROI; presented at Pursuit Demo Day to staff, fellow Builders, and a Fortune 500 reviewer (legal entity formation and IP filings in progress)}
      \resumeItemListEnd
      \smallskip

    \resumeSubheadingEd
      {Architechne $|$ Data Analyst \& Partnership Coordinator (1099)}{Sep. 2025 -- Mar. 2026}
      {Sourced luxury interior-designer, architect, and residential-developer leads for a NYC design partnership business.}{New York, NY}
      \resumeItemListStart
        \resumeItem{}
            {Built a Python + AI web scraper across NYC tri-state directories and designed a MySQL territory database, cutting manual research time by $\sim$50\%}
      \resumeItemListEnd
      \smallskip

    \resumeSubheadingEd
      {Airbnb $|$ Self-Employed Property Manager (Owner-Operator)}{Jul. 2017 -- Jan. 2020}
      {Ran a short-term-rental business solo for 2.5+ years.}{Flushing, NY}
      \resumeItemListStart
        \resumeItem{}
            {Owned listing, marketing, bookkeeping, vendor coordination, and guest relations end-to-end — the same full-ownership discipline applied to software systems today}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Technical Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {Resona / Wisper $|$ Privacy-First On-Device Voice-to-Text}{2026}
      {Cross-platform desktop dictation app: live streaming + file/YouTube transcription, 100\% on-device via whisper.cpp.}
      {https://github.com/aislingld-pursuit/L2-Clone-Prodject}
      \resumeItemListStart
        \resumeItem{}
            {Built a real-time pipeline (mic $\rightarrow$ cpal $\rightarrow$ energy-VAD $\rightarrow$ incremental Whisper) plus file and YouTube import with zero cloud STT and no accounts; four selectable GPU backends (CUDA / Vulkan / Metal / CPU) from one Tauri 2 + Rust + React codebase}
        \resumeItem{}
            {Designed an Ed25519-signed-license freemium model with correct client-vs-server entitlement gating; hardened SSRF and unsafe-export issues (SEC-001/002); co-developed on a PRD + HEART process and shipped v0.2.0-beta.18 across Windows, macOS, and Linux}
      \resumeItemListEnd
      \smallskip
    \resumeProjectHeading
      {Berkshire Hathaway, Reimagined $|$ UX/UI Redesign}{2025}
      {Conceptual redesign of berkshirehathaway.com synthesizing Apple's HIG with Buffett's 1996 Owner's Manual.}
      {https://github.com/nessaisling-lab/Final-Berkshire-Hathaway-redesign}
      \resumeItemListStart
        \resumeItem{}
            {Built a single-file HTML mockup and Figma spec organized around seven paired design principles, meeting WCAG 2.2 AA accessibility with an 8-section written design rationale}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheadingEd
      {Pursuit $|$ AI-Native Builder (Inaugural Cohort)}{Mar. 2025 -- Present}
      {600+ hour, 7-month in-person intensive shipping production-grade AI products end-to-end.}{Long Island City, NY}
      \resumeItemListStart
        \resumeItem{}
            {Shipped 10+ end-to-end builds and wrote 8+ PRDs; delivered a capstone (Nisaba) at Demo Day to Pursuit staff and a Fortune 500 industry reviewer}
      \resumeItemListEnd
      \smallskip

    \resumeSubheadingShort
      {Per Scholas $|$ IT Support — CompTIA A+, Google IT Support, ServiceNow ITSM}{Grad. Oct. 2025}

    \resumeSubheadingShort
      {Vaughn College $|$ Aircraft Mechanic Airframe \& Powerplant (coursework complete)}{Flushing, NY}

  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills \& Tools}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages \& Frameworks: }
     {Rust (Iced, axum, SQLx, Tauri 2, whisper-rs, cpal), Python, C, C++, Assembly, JavaScript/TypeScript, React, Node, HTML/CSS, SQL (PostgreSQL, MySQL), REST + LLM APIs, WGSL}
   \resumeSubItem{AI \& Tooling: }
     {Claude Code, Cursor, Anthropic + OpenAI APIs, whisper.cpp, RAG, prompt engineering, agentic workflows, Swiss Ephemeris}
   \resumeSubItem{Systems \& Ops: }
     {Linux, Windows, Git/GitHub, GPU backends (CUDA/Vulkan/Metal), Linux device drivers, hardware bring-up, CompTIA A+, LAN/WLAN networking}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
